### 2024-06-30 multiple-regression.qmd
20240629 - fix error

```{r}
#| echo: false
library("apa")

@@

```{r overfittingModel, echo = FALSE, out.width = "100%", fig.align = "center", fig.height = 8, fig.width = 8, fig.cap = "Over-fitting Model in Red Relative to the True Distribution of the Data in Blue."}
#| label: fig-overfittingModel
#| fig-cap: "Over-fitting Model in Red Relative to the True Distribution of the Data in Blue. From @PetersenPrinciplesPsychAssessment."
#| echo: false
#| fig.height: 8
#| fig.width: 8

>>>>

library("MOTE")

@@

```{r}
#| label: fig-overfittingModel
#| fig-cap: "Over-fitting Model in Red Relative to the True Distribution of the Data in Blue. From @PetersenPrinciplesPsychAssessment."
#| echo: false
#| fig.height: 8
#| fig.width: 8
